---
title: "Data Exercise 1"
author: "Lisa de Sousa Dias"
date: "2/3/2019"
output: html_document
---

```{r setup, include=FALSE}
## Sets defaults for R chunks
knitr::opts_chunk$set(echo = TRUE, # echo = TRUE means that your code will show
                      warning=FALSE,
                      message=FALSE,
                      # fig.path='Figs/', ## where to save figures
                      fig.height = 3,
                      fig.width = 3,
                      fig.align = 'center')

## Add any R packages you require. 
## Here are some we will use in 811:
requires <- c("tidyverse", # tidyverse includes dplyr and ggplot2
              "magrittr",
              "foreign",
              "readstata13",
              "here")

## Install any you don't have
to_install <- c(requires %in% rownames(installed.packages()) == FALSE)
install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )

## Load all required R packages
library(tidyverse)
library(ggplot2); theme_set(theme_bw())
library(magrittr)
library(here)
```


```{}
net install PS813_EX1, from(https://faculty.polisci.wisc.edu/weimer/)

PS813_EX1 0720

save "EX1.dta"
```

# 1. A plot of Legislative Activity by Terms in Office

```{r plot_variable}
d <- readstata13::read.dta13("data/EX1.dta")
ggplot(d, aes(y = Leg_Act, x = terms)) + 
  geom_point()

```

```{r correlation_variables}
corXY <- cor(d$Leg_Act, d$terms)
corXY
```
  
The correlation between Legislative Activity and Terms in Office is `corXY`
  
# 2. Estimating linear regression

```{r regression}
model <- lm(d$Leg_Act ~ d$terms)
# summary(model)
alpha <- model$coefficients[1]
beta <- model$coefficients[2]
summary(model)
```
`r alpha` 
`r beta`

# 3. Computing residuals

```{r residuals}
p_Leg_Act <- predict(model)
resid <- d$Leg_Act - p_Leg_Act

```

# 4. Plot of Residuals
```{r plot_residuals, fig.width = 5}
ggplot(d, aes(y = resid, x = terms)) + 
  geom_point() + 
  geom_hline(yintercept = 0) +
  geom_col(alpha = .1, width = .1, position = "dodge") +
  labs(title = "Residuals (Observed - Predicted Legislative Activity)",
       x = "Terms in Office",
       y = "Residuals")
```

# 5. $Cor(Y,\hat{Y})$
```{r correlation_observed_predicted}
correlation <- cor(d$Leg_Act, p_Leg_Act)
```
$Cor(Y,\hat{Y})$ = `r correlation`

# 6. $Cor(Y,\hat{Y})^2$ vs. $R^2$.
```{r correlation_vs_R2}
r2 <- summary(model)$r.squared
```
$R^2$ = `r r2`

# 7. Hypothesis test
\Large

$\beta = 0$ Number of terms in office has no impact on index of legislative activity of state members and number of terms in office

$\beta \neq 0$ Number of terms in office does impact index of legislative activity of state members and number of terms in office

# 8. Discussion

The outputs indicate that alpha is 7.21978 and beta is 0.6058394. Thus, the estimated intercept is 7.21978 and the estimated slope is 0.6058394. Put differently, when the number of terms in office is 0, the predicted index of legislative activity of state assembly members is 7.22. Moreover, for every change in 1 unit (1 term), there is a 0.61 increase in the index on legistalative activity of state assembly members. Finally, given that the p-value from the regression anlysis (0.553) is greater than 0.05, I fail to reject the null hypothesis.  
