---
title: "PS811 Portfolio - The Impact of Private Property Rights on Women's Tenure in Africa"
author: "Lisa de Sousa Dias"
output:
  html_document: 
    toc: true ## table of contents
    code_folding: hide
---
```{r setup, include=FALSE, echo=FALSE}
## Defaults for R chunks
knitr::opts_chunk$set(echo = TRUE, ## echo = TRUE means code will show
                      warning=FALSE, ## supress warnings and messages from R
                      message=FALSE,
                      fig.path='Figs/', ## where to save figures
                      fig.height = 6, ## default figure size (can differ in each chunk)
                      fig.width = 6)

## Add any R packages you require. 
## Here are some we will use in 811:
requires <- c("tidyverse", ## tidyverse includes dplyr and ggplot2
              "magrittr",
              "foreign",
              "here",
              "maps",
              "raster")

## Install any you don't have
to_install <- c(requires %in% rownames(installed.packages()) == FALSE)
install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )

## Load all required R packages
library(tidyverse)
library(ggplot2); theme_set(theme_minimal())
library(magrittr)
library(here)
library(maps)
library(raster)
```

## Research Question 

While land lies at the heart of social, political, and economic life in Africa, women remain disadvantaged and discriminated against in existing land tenure regimes. In Kenya, for example, despite major constitutional and legislative reform, estimates suggest that only 1 per cent of land is registered to women alone and only 5 per cent of land is registered jointly with men. Much of the literature on women and land tenure in Africa focuses on questions surrounding customary land systems and specifically whether they provide greater protections for women. A dominant view in the literature and among policymakers is that land reform should build on customary land systems and existing institutions rather than break with them. These arguments are based on evidence that land titling and registration programs and the erosion of customary systems during and after independence were a setback for women. 

Meanwhile, a growing number of feminist scholars and African women's rights activists have challenged the claim that reforming customary systems advances women's land interests. They claim that reforming customary systems reproduces gendered power imbalances especially evident as customary laws and practices have selectively preserved elements that subordinate women. Indeed, these scholars and activists argue that only right-based land systems and private property rights will enable women to break from the patriarchal power structures of customary land systems. Given contradicting and opposing views, I investigate how private property rights impact women's tenure security using data from 16 countries in sub-Saharan Africa.

## Descriptive Statistics

```{r datasets for map}

world <- map_data("world") %>% rename(country = region)

continent <- raster::ccodes() %>% 
  rename(country = NAME)

world %<>% full_join(continent) # merge world dataset with dataset with continents

world %<>% 
  filter(continent == "Africa") # filter for countries in Africa

landata <- read_csv("data/ssa_sigi_2019.csv") 

landata %<>% 
  mutate(tenure_security = as.numeric(tenure_security)) # transforming Tenure_Security into a numeric variable 

landata %<>% rename(country = country_name) # change Country_Name to country 

landata %>%  # changing name of Ivory Coast and DRC to match 
  mutate(country = str_replace(country, "Ivory Coast" , "Côte d'Ivoire")) %>%
  mutate(country = str_replace(country, "DRC" , "Democratic Republic of the Congo"))

world %<>% full_join(landata) # joining world and landdata 

```

### Share of Labor Force Employed in Agriculture 
```{r share of labor force in agriculture}

# Map of share of labor force employed in agriculture 

world %>%  
  ggplot( aes(x = long, y = lat) ) +  
  geom_polygon( aes(group = group, fill = share_labor_agriculture), color = "grey") +
  scale_fill_viridis_c()

```

### Women's Tenure Security 
```{r women tenure security}

# Map of women's tenure security   

world %>%  
  ggplot( aes(x = long, y = lat) ) +  
  geom_polygon( aes(group = group, fill = tenure_security), color = "grey") +
  scale_fill_viridis_c()

```

### Strength of Private Property Rights
```{r private property rights}

# Map of property rights

world %>%  
  ggplot( aes(x = long, y = lat) ) +  
  geom_polygon( aes(group = group, fill = property_rights), color = "grey") +
  scale_fill_viridis_c()

```

## Analysis 

### OLS Regression

$y_i = \beta_0 + \beta_1*PropertyRights_i + \beta_2*Corruption + \beta_3*ArableLand + \beta_4*LaborAgriculture + \beta_5*GDP + \beta_6*RuralPop +\epsilon_i$

```{r regression}

# OLS regression

d <- landata

model <- lm(d$tenure_security ~ d$property_rights + d$arable_land + d$share_labor_agriculture + d$cpi_score + d$rural_population)

summary(model)
```

### Plot of Residuals 

```{r residuals}

# Plot of residuals

residuals.model <- resid(model)

plot(d$property_rights, residuals.model,
     ylab = "Residuals", xlab = "Property Rights",
     main = "Residuals") +
  abline(0,0)

```

### Case-Study of Kenya - Logistic Model 

```{r case study of kenya}

kenya <- read_csv("data/Kenya_download_V1.csv")

kenya %<>% 
  rename(country = Q3) %>%
  rename(sex = Q21_Gender) %>%
  rename(formaldocs = Q55_any_formal) %>%
  rename(tenuresecurity = Q45_security)

myvariables <- c("country", "sex", "formaldocs", "tenuresecurity")

kenyadata <- kenya[myvariables]

m2 <- glm(factor(tenuresecurity) ~ formaldocs*sex, data = kenyadata, family = "binomial")

summary(m2)

```

## Data Sources

- Social Institutions and Gender Index ( [data](https://www.genderindex.org/data/) )
- Transparency International Corruption Perception Index ( [data](https://www.transparency.org/cpi2018) )
- Prindex data on perceptions of land and property rights ( [data](https://www.prindex.net/data/) )
- World Bank indicators ( [data](https://datacatalog.worldbank.org/dataset/world-development-indicators) )

