---
title: "PS811 Portfolio"
author: "Lisa de Sousa Dias"
output:
  html_document: 
    toc: true ## table of contents
    code_folding: hide
---
```{r setup, include=FALSE, echo=FALSE}
## Defaults for R chunks
knitr::opts_chunk$set(echo = TRUE, ## echo = TRUE means code will show
                      warning=FALSE, ## supress warnings and messages from R
                      message=FALSE,
                      fig.path='Figs/', ## where to save figures
                      fig.height = 6, ## default figure size (can differ in each chunk)
                      fig.width = 6)

## Add any R packages you require. 
## Here are some we will use in 811:
requires <- c("tidyverse", ## tidyverse includes dplyr and ggplot2
              "magrittr",
              "foreign",
              "here",
              "maps",
              "raster")

## Install any you don't have
to_install <- c(requires %in% rownames(installed.packages()) == FALSE)
install.packages(c(requires[to_install], "NA"), repos = "https://cloud.r-project.org/" )

## Load all required R packages
library(tidyverse)
library(ggplot2); theme_set(theme_minimal())
library(magrittr)
library(here)
library(maps)
library(raster)
```

## Research Question 

Much of the literature on women and land tenure has focused of questions surrounding customary land systems and specificaly whether they provide greater protections for women. A dominant view in the literature and among policymakers is that land reform should build on custoamry land systems and existing instituions rather than break with them. These arguments are based on evidence that land titiling and registration programs and the erosion of custormary systems during and after independence were negative for women. More recently, a growing number of feminist scholars and African women's rights activists have challenged the claim that reforming customary systems advances women's land interets. This view argues that only right-based land systems and formal property rights will enable women to break from the patriarchal power structutures of customary land systems. Using data for 16 countries in Sub-Saharan Africa, I investigate how formal property rights impact women's tenure security in Sub-Saharan Africa. 

## Data Sources 

## Descriptive Statistics

# Maps 

```{r map tenure security}

world <- map_data("world") %>% rename(country = region)

continent <- raster::ccodes() %>% 
  rename(country = NAME)

world %<>% full_join(continent) # merge world with dataset with continents

world %<>% 
  filter(continent == "Africa") # filter for countries in Africa

landata <- read_csv("data/Africa_Prindex.csv") 

names(landata) <- landata[1, ] 

landata %<>% 
  .[-1, ] %>% # removing the first row which is just empty 
  mutate(Tenure_Security = as.numeric(Tenure_Security)) # transforming Tenure_Security into a numeric variable 

landata %<>% rename(country = Country_Name) # change Country_Name to country 

landata %>%  # changing name of Ivory Coast and DRC to match 
  mutate(country = str_replace(country, "Ivory Coast" , "Côte d'Ivoire")) %>%
  mutate(country = str_replace(country, "DRC" , "Democratic Republic of the Congo"))

landata %<>%
  rename(Security = Tenure_Security) %>%
  rename(Rights = Property_Rights)

world %<>% full_join(land2)

# Ploting world map with Tenure Secuirty

world %>%  
  ggplot( aes(x = long, y = lat) ) +  
  geom_polygon( aes(group = group, fill = Security), color = "grey") +
  scale_fill_viridis_c()

```

```{r map formal rights}

world %>%  
  ggplot( aes(x = long, y = lat) ) +  
  geom_polygon( aes(group = group, fill = Rights), color = "grey") +
  scale_fill_viridis_d()

```

## Analysis 

# Linear Model 
# Logistic Model 

